Progress Report

### 2020-09-03 documentation/Optimization Work/08_27_20.tex
testing with complex conjugate for basic test

E\left[ trace\left((\vs - \mathbf{H}\mathbf{F}\vs)(\vs - \mathbf{H}\mathbf{F}\vs)^H \right)\right]

@@

Assuming $\mathbf{H}$ and $\mathbf{F}$ to be constant over a coherence period, the expectation applies only to $\vs \vs^H$ to give

@@

trace\left((\vs - \mathbf{H}\mathbf{F}\vs)(\vs - \mathbf{H}\mathbf{F}\vs)^H \right).

@@

First we consider equal power allocation at the transmitter such that after finding the first $K \leq N_S$ IRS channels $\mathbf{h}_{2,i}\mathbf{h}^T_{1,i}$, the optimization problem
is given by

@@

	    & \; trace\left((\mI - \mathbf{A}\mathbf{A}^H)
	   (\mI - \mathbf{A}\mathbf{A}^H)^H \right)

@@

	with $\mathbf{A} = (\mG +  \mH_1 + \Sigma_{i=1}^{K} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})$ (to fit on page).

@@

\bibliography{bibliography}
\end{document}

>>>>

E\left[ \trace\left((\vs - \mathbf{H}\mathbf{W}\vs)(\vs - \mathbf{H}\mathbf{W}\vs)^H \right)\right]

@@

Assuming $\mathbf{H}$ and $\mathbf{W}$ (The Tx linear precoder) to be constant over a coherence period, the expectation applies only to $\vs \vs^H$ 
and we consider equal power allocation at the transmitter such that the utility function becomes

@@

\trace\left((\mI - \mathbf{H}\mathbf{W})(\mI - \mathbf{H}\mathbf{W})^H \right).

@@

After finding the first $K \leq N_S$ IRS channels $\mathbf{h}_{2,i}\mathbf{h}^T_{1,i}$, the optimization problem with respect to the IRS phases for the case of a Matched Filter at the Tx is given by

@@

	    & \; \trace\left((\mI - \mathbf{H}\mathbf{H}^H)
	   (\mI - \mathbf{H}\mathbf{H}^H)^H \right)

@@

	or further simplified into
	    & \; - 2 \trace \left( \mathbf{H}\mathbf{H}^H\right) + \trace\left(\mathbf{H}\mathbf{H}^H \mathbf{H}\mathbf{H}^H\right)
	\end{align}\label{mse_problem_s}
	with $\mathbf{H} = (\mG +  \mH_1 + \Sigma_{i=1}^{K} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})$ (to fit on page).

@@

\begin{enumerate}
\item
	Always compare to the matched filter with random phases
\end{enumerate}
\bibliography{bibliography}
\end{document}
